
#########################
#Intra-Thalamic Analysis#
#########################

# Load packages and initialize functions
```{r Initialize functions, warning=FALSE}
library(dplyr)
library(ggplot2) 
library(tidyr)
library(reshape2)
library(circlize)
library(ggthemes)

# Initialize functions
num_edges_list <- c(0, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 
                    0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4)

equal_thresholding_of_matrix <- function(matrix) {
  num_edges_list <- c()
  graph_list <- list()
  threshold_values <- c(0, 0.025, 0.05, 0.075, 0.1, 0.125, 0.15, 0.175, 
                    0.2, 0.225, 0.25, 0.275, 0.3, 0.325, 0.35, 0.375, 0.4)
  for (i in threshold_values) {
    
    matrix[matrix < i] <- 0
    graph <- graph_from_adjacency_matrix(matrix, mode = "undirected", weighted = TRUE, diag = FALSE)
    graph_list[[length(graph_list) + 1]] <- graph
  }
  return(graph_list)
}

graph_metrics_across_densities <- function(graph_list) {
  
  glob_eff_list <- numeric(length(graph_list))
  avg_str_list <- numeric(length(graph_list))
  mod_list <- numeric(length(graph_list))
  
  
  for (i in 1:length(graph_list)) {
    inv_graph <- graph_list[[i]]
    E(inv_graph)$weight <- 1 / E(inv_graph)$weight
    
    glob_eff_list[i] <- efficiency(inv_graph, type = "global")
    avg_str_list[i] <- mean(strength(graph_list[[i]], mode = "all"))
    
    community <- cluster_louvain(graph_list[[i]])
    membership <- membership(community)
    mod_list[i] <- modularity(graph_list[[i]],
                              membership = membership,
                              weights = E(graph_list[[i]])$weight)
  }
  graph_metrics_list <- c(list(glob_eff_list), list(avg_str_list), list(mod_list))
                          
  return(graph_metrics_list)
}

node_metrics_across_densities <- function(graph_list) {
  num_nodes <- vcount(graph_list[[1]]) 
  num_graphs <- length(graph_list)
  num_measures <- 4
  
  graph_metrics_list <- array(NA, dim = c(num_nodes, num_graphs, num_measures))
  
  node_str_list <- list()
  close_cen_list <- list()
  eigen_cen_list <- list()
  btwn_cen_list <- list()

  for (i in 1:num_graphs) {
    inv_graph <- graph_list[[i]]
    E(inv_graph)$weight <- 1 / E(inv_graph)$weight

    node_str_list[[i]] <- strength(graph_list[[i]], mode = "all")
    close_cen_list[[i]] <- closeness(inv_graph, mode = "all")
    eigen_cen_list[[i]] <- eigen_centrality(graph_list[[i]])$vector
    btwn_cen_list[[i]] <- betweenness(inv_graph, directed = FALSE, 
                            weights = inv_graph$weight)

  }
  
  # Convert lists to matrices
  node_str_matrix <- do.call(cbind, lapply(node_str_list, as.numeric))
  close_cen_matrix <- do.call(cbind, lapply(close_cen_list, as.numeric))
  eigen_cen_matrix <- do.call(cbind, lapply(eigen_cen_list, as.numeric))
  btwn_cen_matrix <- do.call(cbind, lapply(btwn_cen_list, as.numeric))
 
  # Reshape matrices to fit the array dimensions
  for (i in 1:num_graphs) {
    graph_metrics_list[,i,1] <- matrix(node_str_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,2] <- matrix(close_cen_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,3] <- matrix(eigen_cen_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,4] <- matrix(btwn_cen_matrix[,i], nrow = num_nodes)

  }
  return(graph_metrics_list)
}

permutation_test_edge_level <- function(n_permutations = 100000, brain_var = all_brain_names) {
  
  num_nodes <- length(brain_var)
  perm_edge_diff_matrices <- array(NA, dim = c(num_nodes, num_nodes, n_permutations))
  
  for (perm in 1:n_permutations) {
    
    perm_df <- df
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- cor(perm_ptsd_data)
    perm_control_ptsd_matrix <- cor(perm_control_ptsd_data)
    
    perm_edge_diff_matrix <- perm_ptsd_matrix - perm_control_ptsd_matrix
    perm_edge_diff_matrices[,,perm] <- perm_edge_diff_matrix
    
    if (perm %% 2000 == 0) {
      print(paste("Permutation", perm, "completed")) }
  }
  return(perm_edge_diff_matrices)
}

permutation_test_graph_level <- function(n_permutations = 5000, brain_var = all_brain_names) {
  
  num_graph_results <- 3
  
  perm_GE_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))
  perm_str_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))
  perm_mod_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))

  perm_diff_results <- array(NA, dim = c(length(num_edges_list), n_permutations, num_graph_results))

  for (perm in 1:n_permutations) {
  
    perm_df <- df
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- abs(cor(perm_ptsd_data))
    perm_control_ptsd_matrix <- abs(cor(perm_control_ptsd_data))

    perm_ptsd_graph_list <- equal_thresholding_of_matrix(perm_ptsd_matrix)
    perm_control_ptsd_graph_list <- equal_thresholding_of_matrix(perm_control_ptsd_matrix)
    
    perm_ptsd_metrics <- graph_metrics_across_densities(perm_ptsd_graph_list)
    perm_control_ptsd_metrics <- graph_metrics_across_densities(perm_control_ptsd_graph_list)
    
    perm_GE_diff_matrices[, perm] <- perm_ptsd_metrics[[1]] - perm_control_ptsd_metrics[[1]]
    perm_str_diff_matrices[, perm] <- perm_ptsd_metrics[[2]] - perm_control_ptsd_metrics[[2]]
    perm_mod_diff_matrices[, perm] <- perm_ptsd_metrics[[3]] - perm_control_ptsd_metrics[[3]]

    
    if (perm %% 1 == 0) {
       cat(".") }
    if (perm %% 100 == 0) {
      cat("\n")
      print(paste("Permutation", perm, "completed")) }
  }
  perm_diff_results[,,1] <- perm_GE_diff_matrices
  perm_diff_results[,,2] <- perm_str_diff_matrices
  perm_diff_results[,,3] <- perm_mod_diff_matrices

  return(perm_diff_results)
}


permutation_test_node_level <- function(n_permutations = 1000, brain_var = all_brain_names) {
  
  num_nodes <- length(brain_var)
  num_graphs <- length(num_edges_list)
  num_results <- 4
  
  perm_diff_results <- array(NA, dim = c(num_nodes, num_graphs, n_permutations, num_results))
  
  for (perm in 1:n_permutations) {
    
    perm_df <- df
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- abs(cor(perm_ptsd_data))
    perm_control_ptsd_matrix <- abs(cor(perm_control_ptsd_data))
    
    perm_ptsd_graph_list <- equal_thresholding_of_matrix(perm_ptsd_matrix)
    perm_control_ptsd_graph_list <- equal_thresholding_of_matrix(perm_control_ptsd_matrix)
    
    perm_ptsd_metrics <- node_metrics_across_densities(perm_ptsd_graph_list)
    perm_control_ptsd_metrics <- node_metrics_across_densities(perm_control_ptsd_graph_list)
    
    perm_diff_results[, , perm ,] <- perm_ptsd_metrics - perm_control_ptsd_metrics
    
    if (perm %% 1 == 0) {
       cat(".") }
    if (perm %% 100 == 0) {
      cat("\n")
      print(paste("Permutation", perm, "completed")) }
  }

  return(perm_diff_results)
}


```
 
# Load data
```{r Load Data}
df <- read.csv("your_data.csv")

#outliers +-2.689 SD for each of the 50 nuclei should be already removed

```

# Create group dataframes
```{r Create group dataframes}
# Filter data for desired network
edge_order <- c("LeftPuI", "RightPuI", "LeftPuL", "RightPuL", 
                "LeftPuA", "RightPuA", "LeftPuM", "RightPuM",
                "LeftMGN", "RightMGN", "LeftLSg", "RightLSg",
                 "LeftLGN", "RightLGN",

                "LeftVPL", "RightVPL", 
                "LeftVLa", "RightVLa", "LeftVLp", "RightVLp",
                "LeftVM", "RightVM",
                "LeftVA", "RightVA", "LeftVAmc", "RightVAmc", 

                "LeftLP", "RightLP", "LeftLD", "RightLD", #4
                "LeftCL", "RightCL", "LeftPc", "RightPc", #5
                "LeftPf", "RightPf", "LeftCM", "RightCM", #6
                
                "LeftMDl", "RightMDl",
                "LeftMDm", "RightMDm", "LeftRe", "RightRe",
                 "LeftCeM", "RightCeM", "LeftPt", "RightPt",
                "LeftAV", "RightAV")

df_brain <- df[, edge_order]
df_var <- df[, c(1:4)]
df <- cbind(df_var, df_brain)
all_brain_data <- df %>% select(LeftPuI:RightAV)
all_brain_names <- names(all_brain_data)

ptsd_group <- df %>% filter(ptsd_dx == 1)
ptsd_group_data <- ptsd_group %>% select(all_of(all_brain_names))

control_ptsd_group <- df %>% filter(ptsd_dx == 0)
control_ptsd_group_data <- control_ptsd_group %>% select(all_of(all_brain_names))
```

# Create correlation matrices and graph objects for each group
```{r Correlation matrices}
library(brainGraph)

ptsd_matrix <- cor(ptsd_group_data)
abs_ptsd_matrix <- abs(ptsd_matrix)
ptsd_graph_list <- equal_thresholding_of_matrix(abs_ptsd_matrix)
ptsd_graph <- graph_from_adjacency_matrix(abs_ptsd_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)

control_ptsd_matrix <- cor(control_ptsd_group_data)
abs_control_ptsd_matrix <- abs(control_ptsd_matrix)
control_ptsd_graph_list <- equal_thresholding_of_matrix(abs_control_ptsd_matrix)
control_ptsd_graph <- graph_from_adjacency_matrix(abs_control_ptsd_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)
```

# Calculate network properties
```{r Network properties, warning=FALSE}
# Graph edge differences
diff_matrix <- ptsd_matrix - control_ptsd_matrix

ptsd_graph_metrics <- graph_metrics_across_densities(ptsd_graph_list)
control_ptsd_graph_metrics <- graph_metrics_across_densities(control_ptsd_graph_list)
ptsd_node_metrics <- node_metrics_across_densities(ptsd_graph_list)
control_ptsd_node_metrics <- node_metrics_across_densities(control_ptsd_graph_list)


# Global measures
obs_GE_diff <- ptsd_graph_metrics[[1]] - control_ptsd_graph_metrics[[1]] 
obs_str_diff <- ptsd_graph_metrics[[2]] - control_ptsd_graph_metrics[[2]]  
obs_mod_diff <- ptsd_graph_metrics[[3]] - control_ptsd_graph_metrics[[3]] 

# Nodal measures
obs_node_str_diff <- ptsd_node_metrics[,,1] - control_ptsd_node_metrics[,,1]
rownames(obs_node_str_diff) <- all_brain_names
obs_node_close_diff <- ptsd_node_metrics[,,2] - control_ptsd_node_metrics[,,2]
rownames(obs_node_close_diff) <- all_brain_names
obs_node_eigen_diff <- ptsd_node_metrics[,,3] - control_ptsd_node_metrics[,,3]
rownames(obs_node_eigen_diff) <- all_brain_names
obs_node_btwn_diff <- ptsd_node_metrics[,,4] - control_ptsd_node_metrics[,,4]
rownames(obs_node_btwn_diff) <- all_brain_names


ptsd_str <- as.data.frame(ptsd_node_metrics[,,1])
rownames(ptsd_str) <- all_brain_names
ptsd_close <- as.data.frame(ptsd_node_metrics[,,2])
rownames(ptsd_close) <- all_brain_names
ptsd_eigen <- as.data.frame(ptsd_node_metrics[,,3])
rownames(ptsd_eigen) <- all_brain_names
ptsd_btwn <- as.data.frame(ptsd_node_metrics[,,4])
rownames(ptsd_btwn) <- all_brain_names

control_str <- as.data.frame(control_ptsd_node_metrics[,,1])
rownames(control_str) <- all_brain_names
control_close <- as.data.frame(control_ptsd_node_metrics[,,2])
rownames(control_close) <- all_brain_names
control_eigen <- as.data.frame(control_ptsd_node_metrics[,,3])
rownames(control_eigen) <- all_brain_names
control_btwn <- as.data.frame(control_ptsd_node_metrics[,,4])
rownames(control_btwn) <- all_brain_names


```

# Permutation tests
```{r Permutation tests, warning=FALSE}
perm_results_edge_level <- permutation_test_edge_level(100000)

perm_results_node_level <- permutation_test_node_level(5000)

perm_results_graph_level <- permutation_test_graph_level(5000)
```

# Calculate p-values
```{r Calculate p-values}
### Graph Edges ###
num_nodes <- length(names(all_brain_data))
index_values <- numeric()
p_stat_edge_matrix <- array(NA, dim = c(num_nodes, num_nodes))
# calculate p-values
for (row in 1:dim(perm_results_edge_level)[1]) {
  for (col in row:dim(perm_results_edge_level)[2]) {
    index_values <- perm_results_edge_level[row, col, ]
    obs_diff <- diff_matrix[row, col]
    p_stat_edge_matrix[row, col] <- mean(abs(obs_diff) <= abs(index_values))
  }
}
colnames(p_stat_edge_matrix) = names(all_brain_data)
rownames(p_stat_edge_matrix) = names(all_brain_data)


p_stat_edge_matrix <- as.data.frame(p_stat_edge_matrix) %>% 
  select(intersect(colnames(.), central_intrathal)) %>% 
  filter(row.names(.) %in% central_intrathal) %>%
  as.matrix()

# FDR correction
fdr_corrected_matrix <- array(NA, dim = c(num_nodes, num_nodes))
fdr_corrected_matrix <- p.adjust(p_stat_edge_matrix, method = "fdr")
fdr_corrected_matrix <- matrix(fdr_corrected_matrix, nrow = nrow(p_stat_edge_matrix), ncol = ncol(p_stat_edge_matrix))
colnames(fdr_corrected_matrix) = colnames(p_stat_edge_matrix)
rownames(fdr_corrected_matrix) = rownames(p_stat_edge_matrix)
full_fdr_matrix <- fdr_corrected_matrix
full_fdr_matrix[lower.tri(full_fdr_matrix)] <-
  t(full_fdr_matrix)[lower.tri(full_fdr_matrix)]

# Print significant p-values
for (i in 1:nrow(fdr_corrected_matrix)) {
  for (j in 1:ncol(fdr_corrected_matrix)) {
    if (!is.na(fdr_corrected_matrix[i, j]) && fdr_corrected_matrix[i, j] < 0.05) {
      cat(rownames(fdr_corrected_matrix)[i], "--", colnames(fdr_corrected_matrix)[j], "| p-value: ", p_stat_edge_matrix[i,j], "| FDR p-value:", fdr_corrected_matrix[i, j], "\n")
    }
  }
}

```

# Graph level p-values
```{r}
p_stat_matrix_GE <- matrix(NA, nrow = 1, ncol = length(num_edges_list))
p_stat_matrix_str <- matrix(NA, nrow = 1, ncol = length(num_edges_list))
p_stat_matrix_mod <- matrix(NA, nrow = 1, ncol = length(num_edges_list))

for (i in 1:length(num_edges_list)) {
  index_values <- perm_results_graph_level[i,,1]
  p_stat_matrix_GE[i] <- mean(abs(obs_GE_diff[i]) <= abs(index_values))
  index_values <- perm_results_graph_level[i,,2]
  p_stat_matrix_str[i] <- mean(abs(obs_str_diff[i]) <= abs(index_values))
  index_values <- perm_results_graph_level[i,,3]
  p_stat_matrix_mod[i] <- mean(abs(obs_mod_diff[i]) <= abs(index_values))
}
```

# Node level p-values
```{r}
p_stat_matrix_node_str <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_close <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_eigen <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_btwn <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))


for (i in 1:length(num_edges_list)) {
  index_values1 <- perm_results_node_level[, i, , 1]
  index_values2 <- perm_results_node_level[, i, , 2]
  index_values3 <- perm_results_node_level[, i, , 3]
  index_values4 <- perm_results_node_level[, i, , 4]

  for (row in 1:length(names(all_brain_data))) {
    
    # For node strength
        p_stat_matrix_node_str[row, i] <- mean(abs(obs_node_str_diff[row, i]) <= abs(index_values1[row, ]), na.rm = TRUE)


    # For node closeness
        p_stat_matrix_node_close[row, i] <- mean(abs(obs_node_close_diff[row, i]) <= abs(index_values2[row, ]), na.rm = TRUE)


    # For node eigenvector
    p_stat_matrix_node_eigen[row, i] <- mean(abs(obs_node_eigen_diff[row, i]) <= abs(index_values3[row, ]), na.rm=T)

    # For node betweenness
    p_stat_matrix_node_btwn[row, i] <- mean(abs(obs_node_btwn_diff[row, i]) <= abs(index_values4[row, ]), na.rm = TRUE)

    
  }
}

fdr_matrix_node_str <- matrix(NA, nrow = nrow(p_stat_matrix_node_str), ncol = ncol(p_stat_matrix_node_str))
fdr_matrix_node_close <- matrix(NA, nrow = nrow(p_stat_matrix_node_close), ncol = ncol(p_stat_matrix_node_close))
fdr_matrix_node_eigen <- matrix(NA, nrow = nrow(p_stat_matrix_node_eigen), ncol = ncol(p_stat_matrix_node_eigen))
fdr_matrix_node_btwn <- matrix(NA, nrow = nrow(p_stat_matrix_node_btwn), ncol = ncol(p_stat_matrix_node_btwn))


for (i in 1:ncol(p_stat_matrix_node_str)) {
  p_values <- p_stat_matrix_node_str[, i]
  fdr_matrix_node_str[, i] <- p.adjust(p_values, method = "fdr")
  p_values <- p_stat_matrix_node_close[, i]
  fdr_matrix_node_close[, i] <- p.adjust(p_values, method = "fdr")
  p_values <- p_stat_matrix_node_eigen[, i]
  fdr_matrix_node_eigen[, i] <- p.adjust(p_values, method = "fdr")
  p_values <- p_stat_matrix_node_btwn[, i]
  fdr_matrix_node_btwn[, i] <- p.adjust(p_values, method = "fdr")

}

rownames(p_stat_matrix_node_str) <- all_brain_names
rownames(fdr_matrix_node_str) <- all_brain_names
rownames(p_stat_matrix_node_close) <- all_brain_names
rownames(fdr_matrix_node_close) <- all_brain_names
rownames(p_stat_matrix_node_eigen) <- all_brain_names
rownames(fdr_matrix_node_eigen) <- all_brain_names
rownames(p_stat_matrix_node_btwn) <- all_brain_names
rownames(fdr_matrix_node_btwn) <- all_brain_names

```

# Clustering
```{r}
library(cluster)
library(maptree)
library(proxy)
library(scales)
library(ggraph)
library(ggrepel)
library(dendextend)
library(clusteval)
library(RColorBrewer)
library(ggthemes)
library(paletteer)
library(factoextra)
library(genieclust)

pearson_dist <- function(data) {
  as.dist(1 - cor(t(data), method = "pearson"))
}

# Create left and right hemisphere matrices
diff_matrix <- read.csv("diff_matrix.csv", row.names = 1)
tc_diff_matrix <- read.csv("tc_diff_matrix.csv", row.names = 1)
tc_diff_matrix <- tc_diff_matrix[edge_order, ]

tc_diff_matrix1 <- tc_diff_matrix[!startsWith(rownames(tc_diff_matrix), "Left"), ]
rownames(tc_diff_matrix1) <- sub("^Right", "", rownames(tc_diff_matrix1))

diff_matrix1 <- diff_matrix[!startsWith(rownames(diff_matrix), "Left"), ]
rownames(diff_matrix1) <- sub("^Right", "", rownames(diff_matrix1))

tc_diff_matrix2 <- tc_diff_matrix[!startsWith(rownames(tc_diff_matrix), "Right"), ]
rownames(tc_diff_matrix2) <- sub("^Left", "", rownames(tc_diff_matrix2))

diff_matrix2 <- diff_matrix[!startsWith(rownames(diff_matrix), "Right"), ]
rownames(diff_matrix2) <- sub("^Left", "", rownames(diff_matrix2))


#### Clustering ####
thal_dist <-pearson_dist(diff_matrix1)
cx_dist <- pearson_dist(tc_diff_matrix1)

thal_clust <- hclust(thal_dist, method = "average")
cx_clust <- hclust(cx_dist, method = "average")

op_k <- kgs(thal_clust, diss = thal_dist, maxclus = 25, alpha = 1)
which.min(op_k)
op_k2 <- kgs(cx_clust, diss = cx_dist, maxclus = 25, alpha = 1)
which.min(op_k2)

thal_cluster_assignments <- cutree(thal_clust, k = which.min(op_k)+1)
cx_cluster_assignments <- cutree(cx_clust, k = which.min(op_k2)+1)

dend_thal <- as.dendrogram(thal_clust)
dend_cx <- as.dendrogram(cx_clust)

dend_list <- dendlist(dend_thal, dend_cx)

cor_cophenetic(dend_list)
cor(cx_dist,cophenetic(cx_clust))
```



#############################
# Thalamo-Cortical Analysis #
#############################


# Load packages and initialize functions
```{r Initialize functions}
library(dplyr)
library(ggplot2)
library(ggcorrplot)
library(tidyr)

# Initialize functions
num_edges_list <- c(0, 0.025, 0.05, 0.075, 0.1)

equal_thresholding_of_matrix <- function(matrix) {
  num_edges_list <- c()
  graph_list <- list()
  threshold_values <- c(0, 0.025, 0.05, 0.075, 0.1)
  for (i in threshold_values) {
    
    matrix[matrix < i] <- 0
    graph <- graph_from_adjacency_matrix(matrix, mode = "undirected", weighted = TRUE, diag = FALSE)
    graph_list[[length(graph_list) + 1]] <- graph
  }
  return(graph_list)
}

graph_metrics_across_densities <- function(graph_list) {
  
  glob_eff_list <- numeric(length(graph_list))
  avg_str_list <- numeric(length(graph_list))
  mod_list <- numeric(length(graph_list))
  
  for (i in 1:length(graph_list)) {
    inv_graph <- graph_list[[i]]
    E(inv_graph)$weight <- 1 / E(inv_graph)$weight
    
    glob_eff_list[i] <- efficiency(inv_graph, type = "global")
    avg_str_list[i] <- mean(strength(graph_list[[i]], mode = "all"))
    
    community <- cluster_louvain(graph_list[[i]])
    membership <- membership(community)
    mod_list[i] <- modularity(graph_list[[i]],
                              membership = membership,
                              weights = E(graph_list[[i]])$weight)
  }
  graph_metrics_list <- c(list(glob_eff_list), list(avg_str_list), list(mod_list))
                          
  return(graph_metrics_list)
}

node_metrics_across_densities <- function(graph_list) {
  num_nodes <- vcount(graph_list[[1]]) 
  num_graphs <- length(graph_list)
  num_measures <- 4
  
  graph_metrics_list <- array(NA, dim = c(num_nodes, num_graphs, num_measures))
  
  node_str_list <- list()
  close_cen_list <- list()
  eigen_cen_list <- list()
  btwn_cen_list <- list()

  for (i in 1:num_graphs) {
    inv_graph <- graph_list[[i]]
    E(inv_graph)$weight <- 1 / E(inv_graph)$weight

    node_str_list[[i]] <- strength(graph_list[[i]], mode = "all")
    close_cen_list[[i]] <- closeness(inv_graph, mode = "all")
    eigen_cen_list[[i]] <- eigen_centrality(graph_list[[i]])$vector
    btwn_cen_list[[i]] <- betweenness(inv_graph, directed = FALSE, 
                            weights = inv_graph$weight)

  }
  
  # Convert lists to matrices
  node_str_matrix <- do.call(cbind, lapply(node_str_list, as.numeric))
  close_cen_matrix <- do.call(cbind, lapply(close_cen_list, as.numeric))
  eigen_cen_matrix <- do.call(cbind, lapply(eigen_cen_list, as.numeric))
  btwn_cen_matrix <- do.call(cbind, lapply(btwn_cen_list, as.numeric))
 
  # Reshape matrices to fit the array dimensions
  for (i in 1:num_graphs) {
    graph_metrics_list[,i,1] <- matrix(node_str_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,2] <- matrix(close_cen_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,3] <- matrix(eigen_cen_matrix[,i], nrow = num_nodes)
    graph_metrics_list[,i,4] <- matrix(btwn_cen_matrix[,i], nrow = num_nodes)

  }
  return(graph_metrics_list)
}

permutation_test_edge_level <- function(n_permutations = 1000, brain_var = all_brain_names) {
  num_nodes <- length(brain_var)
  perm_edge_diff_matrices <- array(NA, dim = c(50, 68, n_permutations))
  
  for (perm in 1:n_permutations) {
    perm_df <- df
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1)
    perm_ptsd_data <- perm_ptsd_data %>% mutate(cluster = kmc$cluster) %>% filter (cluster == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- cor(perm_ptsd_data)
    perm_ptsd_matrix <- perm_ptsd_matrix[69:118, 1:68]

    perm_control_ptsd_matrix <- cor(perm_control_ptsd_data)
    perm_control_ptsd_matrix <- perm_control_ptsd_matrix[69:118, 1:68]

    perm_edge_diff_matrix <- perm_ptsd_matrix - perm_control_ptsd_matrix
    perm_edge_diff_matrices[,,perm] <- perm_edge_diff_matrix
    
    if (perm %% 100 == 0) {
       cat(".") }
    if (perm %% 1000 == 0) {
      cat("\n")
      cat(paste("Permutation", perm, "completed\n")) }
  }
  return(perm_edge_diff_matrices)
}

permutation_test_graph_level <- function(n_permutations = 1000, brain_var = all_brain_names) {
  perm_df <- df
  num_graph_results <- 4
  
  perm_GE_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))
  perm_str_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))
  perm_mod_diff_matrices <- array(NA, dim = c(length(num_edges_list), n_permutations))

  perm_diff_results <- array(NA, dim = c(length(num_edges_list), n_permutations, num_graph_results))

  for (perm in 1:n_permutations) {
  
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- abs(cor(perm_ptsd_data))
    perm_ptsd_matrix[1:68, 1:68] <- 0
    perm_ptsd_matrix[69:118, 69:118] <- 0
    
    perm_control_ptsd_matrix <- abs(cor(perm_control_ptsd_data))
    perm_control_ptsd_matrix[1:68, 1:68] <- 0
    perm_control_ptsd_matrix[69:118, 69:118] <- 0
    
    perm_ptsd_graph_list <- equal_thresholding_of_matrix(perm_ptsd_matrix)
    perm_control_ptsd_graph_list <- equal_thresholding_of_matrix(perm_control_ptsd_matrix)
    
    perm_ptsd_metrics <- graph_metrics_across_densities(perm_ptsd_graph_list)
    perm_control_ptsd_metrics <- graph_metrics_across_densities(perm_control_ptsd_graph_list)
    
    perm_GE_diff_matrices[, perm] <- perm_ptsd_metrics[[1]] - perm_control_ptsd_metrics[[1]]
    perm_str_diff_matrices[, perm] <- perm_ptsd_metrics[[2]] - perm_control_ptsd_metrics[[2]]
    perm_mod_diff_matrices[, perm] <- perm_ptsd_metrics[[3]] - perm_control_ptsd_metrics[[3]]

    
    if (perm %% 1 == 0) {
       cat(".") }
    if (perm %% 100 == 0) {
      cat("\n")
      cat(paste("Permutation", perm, "completed\n")) }
  }
  perm_diff_results[,,1] <- perm_GE_diff_matrices
  perm_diff_results[,,2] <- perm_str_diff_matrices
  perm_diff_results[,,3] <- perm_mod_diff_matrices

  return(perm_diff_results)
}


permutation_test_node_level <- function(n_permutations = 1000, brain_var = all_brain_names) {
  num_nodes <- length(brain_var)
  num_graphs <- length(num_edges_list)
  num_results <- 4 
  
  perm_diff_results <- array(NA, dim = c(num_nodes, num_graphs, n_permutations, num_results))
  
  for (perm in 1:n_permutations) {
    
    perm_df <- df
    shuffled_labels <- sample(perm_df$ptsd_dx, replace = FALSE)
    perm_df$ptsd_dx <- shuffled_labels
    perm_ptsd_data <- perm_df %>% filter(ptsd_dx == 1) 
    perm_ptsd_data <- perm_ptsd_data %>% mutate(cluster = kmc$cluster) %>% filter (cluster == 1) %>% select(all_of(brain_var))
    perm_control_ptsd_data <- perm_df %>% filter(ptsd_dx == 0) %>% select(all_of(brain_var))
    
    perm_ptsd_matrix <- abs(cor(perm_ptsd_data))
    perm_ptsd_matrix[1:68, 1:68] <- 0
    perm_ptsd_matrix[69:118, 69:118] <- 0

    perm_control_ptsd_matrix <- abs(cor(perm_control_ptsd_data))
    perm_control_ptsd_matrix[1:68, 1:68] <- 0
    perm_control_ptsd_matrix[69:118, 69:118] <- 0

    perm_ptsd_graph_list <- equal_thresholding_of_matrix(perm_ptsd_matrix)
    perm_control_ptsd_graph_list <- equal_thresholding_of_matrix(perm_control_ptsd_matrix)
    
    perm_ptsd_metrics <- node_metrics_across_densities(perm_ptsd_graph_list)
    perm_control_ptsd_metrics <- node_metrics_across_densities(perm_control_ptsd_graph_list)
    
    perm_diff_results[, , perm ,] <- perm_ptsd_metrics - perm_control_ptsd_metrics
    
    if (perm %% 1 == 0) { cat(".")}
    if (perm %% 100 == 0) {
      cat(paste("\nPermutation", perm, "completed")) }
  }

  return(perm_diff_results)
}


```

# Load data
```{r}
df <- read.csv("your_data.csv")

#outliers +-2.689 SD should be already removed
```

# Create group dataframes
```{r}
# Filter data for desired network
#all_brain_data <- df %>% select(Left.Caudate:RightLD)
all_brain_data <- df %>% select(R_bankssts:RightLD)

all_brain_names <- names(all_brain_data)

ptsd_group <- df %>% filter(ptsd_dx == 1)
ptsd_group <- ptsd_group %>% mutate(cluster = kmc$cluster) %>% filter (cluster == 1)
ptsd_group_data <- ptsd_group %>% select(all_of(all_brain_names))

control_ptsd_group <- df %>% filter(ptsd_dx == 0)
control_ptsd_group_data <- control_ptsd_group %>% select(all_of(all_brain_names))
```

# Create correlation matrices and graph objects for each group
```{r}
library(brainGraph)
ptsd_matrix <- cor(ptsd_group_data)
abs_ptsd_matrix <- abs(ptsd_matrix)

abs_ptsd_matrix[1:68, 1:68] <- 0
abs_ptsd_matrix[69:118, 69:118] <- 0

ptsd_graph_list <- equal_thresholding_of_matrix(abs_ptsd_matrix)
ptsd_graph <- graph_from_adjacency_matrix(abs_ptsd_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)

control_ptsd_matrix <- cor(control_ptsd_group_data)
abs_control_ptsd_matrix <- abs(control_ptsd_matrix)

abs_control_ptsd_matrix[1:68, 1:68] <- 0
abs_control_ptsd_matrix[69:118, 69:118] <- 0

control_ptsd_graph_list <- equal_thresholding_of_matrix(abs_control_ptsd_matrix)
control_ptsd_graph <- graph_from_adjacency_matrix(abs_control_ptsd_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)


```

# Calculate network properties
```{r Network properties}
# Graph edge differences
diff_matrix <- ptsd_matrix - control_ptsd_matrix

ptsd_graph_metrics <- graph_metrics_across_densities(ptsd_graph_list)
control_ptsd_graph_metrics <- graph_metrics_across_densities(control_ptsd_graph_list)
ptsd_node_metrics <- node_metrics_across_densities(ptsd_graph_list)
control_ptsd_node_metrics <- node_metrics_across_densities(control_ptsd_graph_list)

# Global measures
obs_GE_diff <- ptsd_graph_metrics[[1]] - control_ptsd_graph_metrics[[1]]
obs_str_diff <- ptsd_graph_metrics[[2]] - control_ptsd_graph_metrics[[2]]
obs_mod_diff <- ptsd_graph_metrics[[3]] - control_ptsd_graph_metrics[[3]]

# Nodal measures
obs_node_str_diff <- ptsd_node_metrics[,,1] - control_ptsd_node_metrics[,,1]
rownames(obs_node_str_diff) <- all_brain_names
obs_node_close_diff <- ptsd_node_metrics[,,2] - control_ptsd_node_metrics[,,2]
rownames(obs_node_close_diff) <- all_brain_names
obs_node_eigen_diff <- ptsd_node_metrics[,,3] - control_ptsd_node_metrics[,,3]
rownames(obs_node_eigen_diff) <- all_brain_names
obs_node_btwn_diff <- ptsd_node_metrics[,,4] - control_ptsd_node_metrics[,,4]
rownames(obs_node_btwn_diff) <- all_brain_names

ptsd_str <- as.data.frame(ptsd_node_metrics[,,1])
rownames(ptsd_str) <- all_brain_names
ptsd_close <- as.data.frame(ptsd_node_metrics[,,2])
rownames(ptsd_close) <- all_brain_names
ptsd_eigen <- as.data.frame(ptsd_node_metrics[,,3])
rownames(ptsd_eigen) <- all_brain_names
ptsd_btwn <- as.data.frame(ptsd_node_metrics[,,4])
rownames(ptsd_btwn) <- all_brain_names

control_str <- as.data.frame(control_ptsd_node_metrics[,,1])
rownames(control_str) <- all_brain_names
control_close <- as.data.frame(control_ptsd_node_metrics[,,2])
rownames(control_close) <- all_brain_names
control_eigen <- as.data.frame(control_ptsd_node_metrics[,,3])
rownames(control_eigen) <- all_brain_names
control_btwn <- as.data.frame(control_ptsd_node_metrics[,,4])
rownames(control_btwn) <- all_brain_names
```

# Permutation test
```{r}
perm_results_edge_level <- permutation_test_edge_level(100000)

perm_results_node_level <- permutation_test_node_level(5000)

perm_results_graph_level <- permutation_test_graph_level(5000)

```

# Calculate p-values
```{r}
### Graph Edges ###
filt_diff_matrix <- diff_matrix[69:118, 1:68]

num_nodes <- length(names(all_brain_data))
index_values <- numeric()
p_stat_edge_matrix <- array(NA, dim = c(dim(perm_results_edge_level)[1],
                                        dim(perm_results_edge_level)[2]))
# calculate p-values
for (row in 1:dim(perm_results_edge_level)[1]) {
  for (col in 1:dim(perm_results_edge_level)[2]) {
    index_values <- perm_results_edge_level[row, col, ]
    obs_diff <- filt_diff_matrix[row, col]
    p_stat_edge_matrix[row, col] <- mean(abs(obs_diff) <= abs(index_values))
  }
}
colnames(p_stat_edge_matrix) = names(all_brain_data)
rownames(p_stat_edge_matrix) = names(all_brain_data)

colnames(p_stat_edge_matrix) = colnames(filt_diff_matrix)
rownames(p_stat_edge_matrix) = rownames(filt_diff_matrix)

p_stat_edge_matrix_modified <- as.data.frame(p_stat_edge_matrix) %>% 
  filter(row.names(.) %in% central_thal) %>%
  as.matrix()

# FDR correction
fdr_corrected_matrix <- array(NA, dim = c(nrow(p_stat_edge_matrix_modified), ncol(p_stat_edge_matrix)))
fdr_corrected_matrix <- p.adjust(as.matrix(p_stat_edge_matrix_modified), method = "fdr")
fdr_corrected_matrix <- matrix(fdr_corrected_matrix, 
                               nrow = nrow(p_stat_edge_matrix_modified), 
                               ncol = ncol(p_stat_edge_matrix))
colnames(fdr_corrected_matrix) = colnames(p_stat_edge_matrix)
rownames(fdr_corrected_matrix) = rownames(p_stat_edge_matrix_modified)

# Print significant p-values
for (i in 1:nrow(fdr_corrected_matrix)) {
  for (j in 1:ncol(fdr_corrected_matrix)) {
    if (!is.na(fdr_corrected_matrix[i, j]) && fdr_corrected_matrix[i, j] < 0.05) {
      cat(rownames(fdr_corrected_matrix)[i], "--", colnames(fdr_corrected_matrix)[j], "| p-value: ", p_stat_edge_matrix_modified[i,j], "| FDR p-value:", fdr_corrected_matrix[i, j], "\n")
    }
  }
}

```

# Graph level p-values
```{r}
p_stat_matrix_GE <- matrix(NA, nrow = 1, ncol = length(num_edges_list))
p_stat_matrix_str <- matrix(NA, nrow = 1, ncol = length(num_edges_list))
p_stat_matrix_mod <- matrix(NA, nrow = 1, ncol = length(num_edges_list))

for (i in 1:length(num_edges_list)) {
  index_values <- perm_results_graph_level[i,,1]
  p_stat_matrix_GE[i] <- mean(abs(obs_GE_diff[i]) <= abs(index_values))
  index_values <- perm_results_graph_level[i,,2]
  p_stat_matrix_str[i] <- mean(abs(obs_str_diff[i]) <= abs(index_values))
  index_values <- perm_results_graph_level[i,,3]
  p_stat_matrix_mod[i] <- mean(abs(obs_mod_diff[i]) <= abs(index_values))
}

```

# Node level p-values
```{r}
p_stat_matrix_node_str <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_close <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_eigen <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))
p_stat_matrix_node_btwn <- matrix(NA, nrow = length(names(all_brain_data)), ncol = length(num_edges_list))


for (i in 1:length(num_edges_list)) {
  index_values1 <- perm_results_node_level[, i, , 1]
  index_values2 <- perm_results_node_level[, i, , 2]
  index_values3 <- perm_results_node_level[, i, , 3]
  index_values4 <- perm_results_node_level[, i, , 4]

  for (row in 1:length(names(all_brain_data))) {
    
    # For node strength
        p_stat_matrix_node_str[row, i] <- mean(abs(obs_node_str_diff[row, i]) <= abs(index_values1[row, ]), na.rm = TRUE)


    # For node closeness
        p_stat_matrix_node_close[row, i] <- mean(abs(obs_node_close_diff[row, i]) <= abs(index_values2[row, ]), na.rm = TRUE)


    # For node eigenvector
    p_stat_matrix_node_eigen[row, i] <- mean(abs(obs_node_eigen_diff[row, i]) <= abs(index_values3[row, ]), na.rm=T)

    # For node betweenness
    p_stat_matrix_node_btwn[row, i] <- mean(abs(obs_node_btwn_diff[row, i]) <= abs(index_values4[row, ]), na.rm = TRUE)

    
  }
}


fdr_matrix_node_str <- matrix(NA, nrow = nrow(p_stat_matrix_node_str), ncol = ncol(p_stat_matrix_node_str))
fdr_matrix_node_close <- matrix(NA, nrow = nrow(p_stat_matrix_node_close), ncol = ncol(p_stat_matrix_node_close))
fdr_matrix_node_eigen <- matrix(NA, nrow = nrow(p_stat_matrix_node_eigen), ncol = ncol(p_stat_matrix_node_eigen))
fdr_matrix_node_btwn <- matrix(NA, nrow = nrow(p_stat_matrix_node_btwn), ncol = ncol(p_stat_matrix_node_btwn))


for (i in seq_len(ncol(p_stat_matrix_node_str))) {
  # Adjust p-values for p_stat_matrix_node_str
  p_values <- p_stat_matrix_node_str[, i]
  adjusted_values <- p.adjust(p_values[69:118], method = "fdr")
  fdr_matrix_node_str[69:118, i] <- adjusted_values

  # Adjust p-values for p_stat_matrix_node_close
  p_values <- p_stat_matrix_node_close[, i]
  adjusted_values <- p.adjust(p_values[69:118], method = "fdr")
  fdr_matrix_node_close[69:118, i] <- adjusted_values

  # Adjust p-values for p_stat_matrix_node_eigen
  p_values <- p_stat_matrix_node_eigen[, i]
  adjusted_values <- p.adjust(p_values[69:118], method = "fdr")
  fdr_matrix_node_eigen[69:118, i] <- adjusted_values

  # Adjust p-values for p_stat_matrix_node_btwn
  p_values <- p_stat_matrix_node_btwn[, i]
  adjusted_values <- p.adjust(p_values[69:118], method = "fdr")
  fdr_matrix_node_btwn[69:118, i] <- adjusted_values
}

rownames(p_stat_matrix_node_str) <- all_brain_names
rownames(fdr_matrix_node_str) <- all_brain_names
rownames(p_stat_matrix_node_close) <- all_brain_names
rownames(fdr_matrix_node_close) <- all_brain_names
rownames(p_stat_matrix_node_eigen) <- all_brain_names
rownames(fdr_matrix_node_eigen) <- all_brain_names
rownames(p_stat_matrix_node_btwn) <- all_brain_names
rownames(fdr_matrix_node_btwn) <- all_brain_names

```
